# PROJECT
----------

*The data for this project is collected from  [Human Activity Recognition database](http://google.com) built from the recordings of 30 subjects performing 6 activities of daily living.
In this project we clean this data using R codes.*

#Activites of different exercises are recorded#


```{r}
activities <- read.table("UCI_HAR_Dataset/activity_labels.txt",sep="",header=FALSE)
colnames(activities) = c("code","name")
print(activities)
```

#features are column names of various measurements

```{r}
features <- read.table("UCI_HAR_Dataset/features.txt.",sep=" ",header=FALSE)
colnames(features) =c("code","name")
head(features)
```

##PREPARING TEST DATA
###subject_test file contains activity ids performed on each person
###x_test contains several columns data of various features
###y_test contains activity ids performed on each person
### Above three files contains same no.of records. First 2 files contains same data

##*subjects*

```{r}
subjects <- read.table("UCI_HAR_Dataset/test/subject_test.txt",sep=" ",header=FALSE)
colnames(subjects)=c("sub_id")
head(subjects)
```

```{r}
tail(subjects)
```

##*act_columns*

```{r}
activity_columns <- read.table("UCI_HAR_Dataset/test/y_test.txt",sep=" ",header=FALSE)
colnames(activity_columns)=c("act_id")
head(activity_columns)
```

```{r}
tail(activity_columns)
```

##*features_col*

```{r}
features_columns <- read.table("UCI_HAR_Dataset/test/x_test.txt",sep="",header=FALSE)
colnames(features_columns)=features$name

library(dplyr)

uniq.columns = unique(colnames(features_columns))
xtest = select(features_columns, uniq.columns)
xtest = select( xtest, contains("std"), contains("Mean"))
head(xtest,1)
```
